### 2016-07-09 paper/numerical_experiments.tex
Minor

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Error Estimate Localization} \label{sec:errLocal}
%------------------------------------------------------------------------------------------------------------------------%
\Cref{alg:refSeries} does not require a particular method for localizing the error estimate. A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element. While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.

We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements. For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$. Note that the error estimate in \cref{eq:finErrExp} can be equivalently written as
%
\begin{equation}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
\end{equation}
%
We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$. Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum_{i\in I}\varphi_i\lambda_i,\sum_{i\in I}\upvarphi_i x_i)$. The error estimate
%
\begin{equation}
\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
\end{equation}
%
where
%
\begin{equation}\label{eq:basisblame}
\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
\end{equation}
%
can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$. The basis functions with the largest error contributions are flagged, and the elements in their support are refined. Using this method, elements in which the high-fidelity model is already being used are not interpreted as continuing to contribute to the error in the QoI and thus are not marked again for refinement. The only exceptions are elements near the interfaces between the low-fidelity and high-fidelity regions, as basis functions near the boundary may have their support divided between the two regions and thus have a nonzero error contribution. 
%------------------------------------------------------------------------------------------------------------------------%
\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega \label{eq:cdvcdrHF_bdry}
\end{align} 
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by, 
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
-42.0 & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.

>>>>

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega \label{eq:cdvcdrHF_bdry}
\end{align} 
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by, 
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
-42.0 & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.
